\plaintitle

### 2016-09-16 drafts/labor/introduction.tex
space issue

\topic{The past decade has seen a flourishing of on--demand work,
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into modular blocks
has allowed people to engage in work despite
limited time,
little to no awareness of the broader context of the work, and 
(often) fleeting identities and associations
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
We've seen on--demand work passing by a number of aliases:
as \textit{crowd work} --- on platforms such as Amazon Mechanical Turk (AMT) and other sites of (predominantly) information work;
as \textit{gig work} --- typically involving platforms for one--off jobs, like driving, courier services, etc\dots;
as the \textit{sharing economy} --- where participants can rent out their valuables (such as a car, a home, etc\dots)on an ad hoc basis when they don't need it.
The realization
that complex tasks can be accomplished by directing and managing crowds of workers
has spurred the research and industry communities to flock to sites of labor
like AMT
to explore the limits of this distributed, on--demand workforce.
Researchers have taken to the space in earnest,
finding opportunities to enable new forms of work
using this population of ``Turkers''
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

>>>>

\topic{The past decade has seen a flourishing of on--demand work,
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into modular blocks
has allowed people to engage in work despite
limited time,
little to no awareness of the broader context of the work, and 
(often) fleeting identities and associations
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
We've seen on--demand work passing by a number of aliases:
as \textit{crowd work} --- on platforms such as Amazon Mechanical Turk (AMT) and other sites of (predominantly) information work;
as \textit{gig work} --- typically involving platforms for one--off jobs, like driving, courier services, etc\dots;
as the \textit{sharing economy} --- where participants can rent out their valuables (such as a car, a home, etc\dots)
on an ad hoc basis when they don't need it.
The realization
that complex tasks can be accomplished by directing and managing crowds of workers
has spurred the research and industry communities to flock to sites of labor
like AMT
to explore the limits of this distributed, on--demand workforce.
Researchers have taken to the space in earnest,
finding opportunities to enable new forms of work
using this population of ``Turkers''
\cite{bernsteinSoylent,redballoon,paolacci2010running}.
